Variational Monte Carlo on bosonic systems

### 2018-01-22 project_1/article/article.tex
Add introduction to the project
Use Revtex for article

\documentclass[12pt, a4paper]{article}

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Nice fonts for nice people
\usepackage[sc, osf]{mathpazo}
\linespread{1.025} % Make more room for Palatino font
\usepackage[euler-digits, small]{eulervm}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include package for drawing Feynman diagrams
\usepackage{tikz-feynman}
% Include package for typesetting contractions
\usepackage{simpler-wick}
% Include the Feynman-slash
\usepackage{slashed}
% Include Tikz
\usepackage{tikz}
% Make Latex a bit wider
\usepackage[a4paper, total={6in, 8in}]{geometry}

@@

\title{Variational Monte Carlo on bosonic systems\\FYS4411}
\author{
    Winther-Larsen, Sebastian Gregorius
    \and
    Schøyen, Øyvind Sigmundson}
\date{\today}

@@

@@

Start

>>>>

\documentclass[
    a4paper, aps, twocolumn, floatfix, superscriptaddress]{revtex4-1}

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include package for drawing Feynman diagrams
\usepackage{tikz-feynman}
% Include package for typesetting contractions
\usepackage{simpler-wick}
% Include the Feynman-slash
\usepackage{slashed}
% Include Tikz
\usepackage{tikz}

@@

@@

\title{Variational Monte Carlo on bosonic systems}
\author{Winther-Larsen, Sebastian Gregorius}
\affiliation{University of Oslo}
\author{Schøyen, Øyvind Sigmundson}
\affiliation{University of Oslo}
\date{\today}

@@

\section{Introduction}
    We will in this project study the Variational Monte Carlo (VMC) method, and
    use it to evaluate the ground state energy of a trapped, hard sphere Bose
    gas.
